\begin{thebibliography}{10}
\providecommand{\url}[1]{{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{DOI~\discretionary{}{}{}#1}\else
  \providecommand{\doi}{DOI~\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem{BastianBlattDednerEngwerKloefkornKornhuberOhlbergerSander2008}
Bastian, P., Blatt, M., Dedner, A., Engwer, C., Klöfkorn, R., Kornhuber, R.,
  Ohlberger, M., Sander, O.: A generic grid interface for parallel and adaptive
  scientific computing. {Part II}: Implementation and tests in dune. computing.
\newblock Computing \textbf{82}(2--3), 121--138 (2008)

\bibitem{BastianBlattDednerEngwerKloefkornOhlbergerSander2008}
Bastian, P., Blatt, M., Dedner, A., Engwer, C., Klöfkorn, R., Ohlberger, M.,
  Sander, O.: A generic grid interface for parallel and adaptive scientific
  computing. {Part I}: Abstract framework.
\newblock Computing \textbf{82}(2--3), 103--119 (2008)

\bibitem{BlattBastian2007}
Blatt, M., Bastian, P.: The iterative solver template library.
\newblock In: B.~Kåström, E.~Elmroth, J.~Dongarra, J.~Wasniewski (eds.)
  Applied Parallel Computing. State of the Art in Scientific Computing,
  \emph{Lecture Notes in Scientific Computing}, vol. 4699, pp. 666--675.
  Springer (2007)

\bibitem{dune}
DUNE, the Distributed and Unified Numerics Environment.
\newblock \url{http://www.dune-project.org/}

\bibitem{boost}
Boost: {C++} libraries.
\newblock \url{http://www.boost.org/}

\bibitem{DeuflhardWeiserBook}
Peter Deuflhard, Martin Weiser:
Numerische Mathematik 3. Adaptive L\"{o}sung partieller Differentialgleichungen.
\newblock de Gruyter, 2011.

\bibitem{DdBook2006}
Deuflhard, P.: Newton Methods for Nonlinear Problems. Affine Invariance and
 Adaptive Algorithms.
\newblock \emph{Series Computational Mathematics}, vol. 35, Springer (2006)

\bibitem{DeuflhardLeinenYserentant89}
Deuflhard, P., Leinen, P., Yserentant, H.: Concepts of an adaptive hierarchical
  finite element code.
\newblock IMPACT Comp. Sci. Eng. \textbf{1}(1), 3--35 (1989)

\bibitem{DeuflhardNowak1987}
Deuflhard, P., Nowak, U.: Extrapolation integrators for quasilinear implicit
  {ODEs}.
\newblock In: P.~Deuflhard, B.~Engquist (eds.) Large Scale Scientific
  Computing, \emph{Progress in Scientific Computing}, vol.~7, pp. 37--50.
  Birkh\"{a}user (1987)

\bibitem{GoetschelWeiserSchiela10}
G\"{o}tschel, S., Weiser, M., Schiela, A.: Solving optimal control problems 
with the Kaskade7 Finite Element Toolbox.
\newblock In: Dedner, Flemisch, Kl\"{o}fkorn (eds.) Advances in DUNE, pp. 101--112.
Springer (2012), see also ZIB Report 10-25 (2010)

\bibitem{HinzeEtAl09}
Hinze, M., Pinnau, R., Ulbrich, M., Ulbrich, S.: Optimization with {PDE}
  constraints.
\newblock Springer, Berlin (2009)

\bibitem{KaelbererPolthierTycowicz09}
K\"{a}lberer, F., Polthier, K., von Tycowicz, C.: Lossless compression of
  adaptive multiresolution meshes.
\newblock In: Proc. Brazilian Symposium on Computer Graphics and Image
  Processing (SIBGRAPI), vol.~22 (2009)

\bibitem{Logg2007}
Logg, A.: Automating the finite element method.
\newblock Arch Comput Methods Eng \textbf{14}, 93--138 (2007)

\bibitem{Martin79}
Martin, G.: Range encoding: an algorithm for removing redundancy from a
  digitised message.
\newblock Presented at Video \& Data Recording Conference, Southampton (1979)

\bibitem{NocedalWright06}
Nocedal, J., Wright, S.J.: Numerical Optimization.
\newblock Springer, New York (2006)

\bibitem{SchGue2009}
Schiela, A., G\"unther, A.: Interior point methods in function space for state
  constraints -- {I}nexact {N}ewton and adaptivity.
\newblock ZIB Report 09-01 (2009)

\bibitem{ugPackage}
UG, software package for solving partial differential equations.
\newblock \url{http://atlas.gcsc.uni-frankfurt.de/~ug/index.html}

\bibitem{Veldhuizen1995}
Veldhuizen, T.: Using {C++} template metaprograms.
\newblock C++ Report \textbf{7}(4), 36--43 (1995)

\bibitem{WeiserGoetschel10}
Weiser, M., G\"{o}tschel, S.: State trajectory compression for optimal control
  with parabolic {PDEs}.
\newblock ZIB Report 10-05 (2010)

\bibitem{WeiserGaenzlerSchiela2008}
Weiser, M., Gänzler, T., Schiela, A.: Control reduced primal interior point
  methods.
\newblock Comput Optim Appl \textbf{41}(1), 127--145 (2008)

\bibitem{Zumbusch1995}
Zumbusch, G.: Symmetric hierarchical polynomials and the adaptive h-p-version.
\newblock In: A.~Ilin, L.~Scott (eds.) Proc. of the Third Int. Conf. on
  Spectral and High Order Methods, ICOSAHOM '95, Houston Journal of
  Mathematics, pp. 529--540 (1996)

\end{thebibliography}
